Latitudinal gradients in niche breadth vary across ecosystem types.

### 2015-09-02 manuscript/latitudepaper.tex
Small changes

  If this is the case, it may still be possible to uncover effects of latitude
  on specialisation by examining the shape of the scaling  relationship
  between specialisation and species richness over changing latitude. Here, we
  use three measures of specialisation: mean links per species, mean
  generality (number of prey), and mean vulnerability (number of predators).
  By testing whether latitude affects the scaling of each property with
  species richness, we test for the effects of latitude on specialisation
  implied by the ``latitude-niche breadth hypothesis''. If the scaling of
  specialisation with species richness is weaker at the tropics (i.e., if
  species gain fewer links, predators, or prey as the size of the network
  increases), this will indicate narrower niches at the tropics. If, however,
  the scaling of specialisation with species richness does not vary over
  latitude, this will indicate that niches are similarly-sized
  worldwide but that there is a broader niche space in the tropics.

>>>>

  If this is the case, it may still be possible to uncover effects of latitude
  on specialisation by examining the shape of the scaling  relationship
  between specialisation and species richness over changing latitude. As
  food webs describing different ecosystem types may differ both in their
  food-web structure~\cite{Dunne2004,Shurin2006} and in the extent to [[seasonal
  variation? Latitudinal gradients in S? Productivity? whatnow?]], we also included
  ecosystem type as a covariate.   Here, we
  use three measures of specialisation: mean links per species, mean
  generality (number of prey), and mean vulnerability (number of predators).
  By testing whether latitude affects the scaling of each property with
  species richness, we test for the effects of latitude on specialisation
  implied by the ``latitude-niche breadth hypothesis''. If the scaling of
  specialisation with species richness is weaker in the tropics (i.e., if
  species gain fewer links, predators, or prey as the size of the network
  increases), this will indicate narrower niches at the tropics. If, however,
  the scaling of specialisation with species richness does not vary over
  latitude, this will indicate that niches are similarly-sized
  worldwide but that there is a broader niche space in the tropics.
